---
output: github_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "##",
  fig.path = "man/images/"
)
```

# quanteda.plagiarism

A tool to detect text segments that are very similar to other segments. Useful in studying flows of information or detecting plagiarism. This is an example of **quanteda** extension package for ECPR summer school. 

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("koheiw/quanteda.plagiarism")
```


```{r message=FALSE}
require(quanteda)
require(quanteda.plagiarism)

quanteda_options(threads = 8)
corp <- data_corpus_inaugural
toks <- tokens(corp, remove_punct = TRUE) %>%
    tokens_remove(stopwords("en")) %>%
    tokens_select("^[\\p{L}]+$", valuetype = "regex")

```

In this example, `textstat_plagiarism()` detects 5-word segments of texts in the modern US presidents' speeches, `tail(toks, 20)`, that are similarit (cosine >= 0.7) to ealier presidents' speeches, `head(toks, 20)`. It seems that Jefferson's 1801 speech inspired many of the modern presidents (or their speech writers).

```{r}
tstat_plag <- textstat_plagiarism(
    tail(toks, 20),
    head(toks, 20),
    size = 5,
    min_simil = 0.7
)
mat <- as.matrix(tstat_plag, upper = FALSE)
print(mat)
colSums(mat)
```

These are segments that are similar to those in ealier speeches.

```{r}
as.list(tstat_plag, upper = FALSE) %>% tail(10)
```
